NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/appendix_modelDescription.tex
update module name

The Decomposable Attention~\cite{parikh2016emnlp} model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels. The pipeline can be separated into three phases: encoder, attention and classifier. Here we briefly formalize these three layers.

@@

\section{Appendix B: Code Example: Link Visualization with Model}
From the user point of view, the following python script is all the code the domain expert needs to link the NLP model with the visual interface. The visualization library's API defines several callbacks (call Hook in the code) that describe the model functionality (e.g., prediction) need to be supplied by the NLP model.

\begin{lstlisting}[language=Python, caption=Code for generating the visualization.]
from nlize import *
from modelInterface import *
from sentenceGenerator import *

>>>>

The Decomposable Attention~\cite{parikh2016emnlp} model is an end-to-end model that takes vectorized premise sentence and hypothesis sentence, and output a probability distribution over three labels. The pipeline can be separated into three phases: encoder, attention and classifier. Here we briefly formalize these three layers (referred to as stages in the main text of the paper).

@@

\section{Appendix B: Code Example: Link Visualization with Model}
From the user's point of view, the following Python script is all the code the domain expert needs to link the NLP model with the visual interface and set up the visualization system shown in the paper. The visualization library's API defines several callbacks (called ``Hook'' in the API) that correspond to functions (e.g., prediction) need to be supplied by the NLP model.

\begin{lstlisting}[language=Python, caption=Code for setting up the visualization system shown in the paper.]
from nlize import *
from modelInterface import *
from sentenceGenerator import *
